What is confining the proplyd bow shocks in Orion?

### 2016-12-09 papers/Paper1/quadrics-appendix.tex
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote

For the sake of completness, in this section we develop the particular case of the parabola.
The parametrization is given by:

@@

Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and (\ref{eq:z-par-a}) we find that:

@@

The projected radius $R'_0$ can be computed as $x'(y'=0)$. The value of $t$ which fullfill this condition is $t_\parallel$, so:

\begin{align}
t_\parallel &= \tan i \\
\frac{R'_0}{D'} &= \frac{R_0}{D}\left(1-\frac{1}{2}A\tan^2 i\right)  
\end{align}

>>>>

In this section we develop the particular case of the parabola.
The parametrization is given by:

@@

Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and (\ref{eq:z-par-a}) we find the apparent shape
of the paraboloid:

@@

Taking the limit of eqautions () and () when $\theta_c$ tends to zero we find that:

\begin{align}
\left(\frac{q'}{q}\right)_{parabola} &= 1+\frac{A\tan^2 i}{2}\\
\left(A'\right)_{parabola} &= \frac{A}{\cos^2 i + \frac{A}{2}\sin^2 i}
\end{align}

### 2016-12-09 papers/Paper1/sec-conic.tex
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can
do the following parametrization\footnote{The wholee formalism descripted in this section does
  not apply for paraboloids ($\theta_c=0$ case). This case is developed in appendix
  \ref{app:parabola}}:
\begin{align}
x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 &= a - x_0 \\
a<0 ~ \mathrm{for~hyperbola}
\end{align}
We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
a parabola.
To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,\theta_c)$
could be derived from the former. The transformation between the conic parameters and the characteristic radii are given by:
\begin{align}
R_c &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
R_{90} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
\end{align}
In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric. The inverse transformation of (\ref{eq:Rc-conic})
and (\ref{eq:r90-conic}) is given by:
\begin{align}
\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
A &\equiv \frac{R_c}{R_0}
\end{align}

@@

Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y-2}) we find that
\begin{align}
a' &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
\Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \\
b' &= b
\end{align}

>>>>

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization
\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
  projected shape are developed in appendix \ref{app:parabola}}:
\begin{align}
x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 &= a - x_0 \\
a<0 ~ \mathrm{for~hyperbola}
\end{align}
We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
a parabola.
To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,\theta_c)$
could be derived from the former. The transformation between the conic parameters and the characteristic radii are given by:
\begin{align}
R_c &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
R_{90} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
\end{align}
In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric. The inverse transformation of (\ref{eq:Rc-conic})
and (\ref{eq:r90-conic}) is given by:
\begin{align}
\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
A &\equiv \frac{R_c}{R_0}
\end{align}

@@

Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y-2}) we find that
\begin{align}
a' &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
\Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \\
b' &= b \label{eq:b-prime}
\end{align}
